UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2014-08-11 paper/proposal-ext.tex
Fixes to first algorithm

\documentclass[11pt]{artikel3}
\usepackage{fullpage, setspace, graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{times}

@@

\begin{itemize}
\item High level software design:
\begin{itemize}
\item Input per single host: 
	\begin{itemize}
	\item Uptime - metric to report how long the system is up. By default, it is gathered as an aggregation of total runtime since reboot. Post-processing of this information will be done to distribute total number of running hours per day to align with pricing model.
	\item Pricing scheme - one of: on-demand, light, medium, heavy - a property of reserved machine that pricing is based on.
	\end{itemize}
\item Analysis: An algorithm that calculates an optimality factor for a given host based on a daily value of Uptime and choice of Pricing scheme.
\item Output: Algorithm results to be send to a graphing system to create dashboards to show current state and optimality ratio.
\end{itemize}
\end{itemize}

>>>>

\documentclass[11pt]{artikel3}
\usepackage{fullpage, setspace, graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

@@

\begin{itemize}
\item High level software design:
\begin{itemize}
\item Input per single host: 
	\begin{itemize}
	\item Uptime - metric to report how long the system is up. By default, it is gathered as an aggregation of total runtime since reboot. Post-processing of this information will be done to distribute total number of running hours per day to align with pricing model.

	\begin{algorithm}[H]
 		\KwData{Timestamp in epoch, Uptime in seconds}
 		\KwResult{total uptime in seconds per hour}
 		\If{Timestamp indicates a start of new hour e.g. 02:00:00 UTC} {
 			set startHour to Timestamp\;
 			set endHour to Timestamp + 1h\;
 			set totalUptime to Uptime\;
 			set initialUptime to Uptime\;
 			set lastUptime to Uptime\;
 			set dived to False\;
 			return;
 		}
 		\eIf{Timestamp is between startHour and endHour} {
 			\If{Uptime is smaller than lastUptime} {
 				totalUptime += lastUptime\;
 				set dived to True\;
 			}
 		} (\textsl{Timestamp equals endHour} \textbf{then} ) 
 		{
 			\eIf{dived} {
 				return totalUptime - initialUptime\;
 				}
 			{
 			return Uptime - initialUptime\;
 			}
 		}
 \caption{Post-processing algorithm to calculate total uptime per hour}
\end{algorithm}

	\item Pricing scheme - one of: on-demand, light, medium, heavy - a property of reserved machine that pricing is based on.
	\end{itemize}
\item Analysis: An algorithm that calculates an optimality factor for a given host based on a daily value of Uptime and choice of Pricing scheme.
\item Output: Algorithm results to be send to a graphing system to create dashboards to show current state and optimality ratio.
\end{itemize}
\end{itemize}
